---
title: "Regression"
author: "Chun-Hui Lin"
date: "2024-10-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

Some notes on generating regression tables from the  [tbl_regression()](https://www.danieldsjoberg.com/gtsummary/articles/tbl_regression.html) and the [finalfit()](https://finalfit.org/articles/all_tables_examples.html) tutorials, setup and detail of example data set are described in the link: 

* Some setups depend on outcome types. You can modify them based on your own data set.

  * Continuous outcomes: linear regression; if outcome is non-normally distributed, consider log-transformation. 
  * Dichotomous outcomes: logistic regression; if outcome is very common (greater than 10%), consider poisson regression with robust error variances. 
  * Ordinal outcomes: multinomial logistic regression; if assuming proportional odds, conduct ordinal logistic regression.

```{r, echo=FALSE, warning=FALSE}
# install.packages('gtsummary'); install.packages('finalfit')
library(gtsummary); library(finalfit)
```

## gtsummary::tbl_regression()

* `tbl_regression()`

  * `exponentiate=` argument: coefficient estimates exponentiate if `TRUE`.
  * `estimate_fun=` argument: ratios round to specified digits.
  
### Linear Regression

```{r}
tbl_regression(lm(age ~ trt + grade, trial), 
               estimate_fun = ~ style_sigfig(.x, digits = 2),
               pvalue_fun = ~ style_pvalue(.x, digits = 2))
```

### Logistic Regression

```{r}
tbl_regression(glm(response ~ trt + age + grade, trial, family = 'binomial'), 
               exponentiate = T,
               estimate_fun = ~ style_ratio(.x, digits = 2),
               pvalue_fun = ~ style_pvalue(.x, digits = 2))
```

### Poisson Regression

* `coeftest()`

  * `vcov=` argument: specify sandwich covariance matrix to obtain robust standard errors.

```{r, warning=FALSE}
tidy_robust(glm(response ~ trt + age + grade, trial, family = 'poisson'), 
            exponentiate = T,
            vcov = sandwich::sandwich,
            estimate_fun = ~ style_ratio(.x, digits = 2),
            pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
  remove_intercept() %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  as.data.frame() %>%
  condense_fit(estimate_name = "RR (robust SE)")
```

## finalfit::finalfit()

* `finalfit()`

  * `metrics=` argument: include model metrics in output if `TRUE`.

### Linear Regression

```{r}
trial %>% 
  finalfit('age', c('trt', 'grade'), 
           metrics = T) #equivalent: lmuni(), lmmulti()
```

### Logistic Regression

```{r, echo=FALSE}
trial$response.factor = factor(trial$response, labels = c('No', 'Yes'))
```

```{r}
trial %>% 
  finalfit('response.factor', c('trt', 'age', 'grade'), 
           metrics = T) #equivalent: glmuni(), glmmulti()
```

### Poisson Regression

```{r}
trial %>% 
  glmmulti('response', c('trt', 'age', 'grade'), family = poisson) %>%
  lmtest::coeftest(., vcov = sandwich::sandwich) %>%
  broom::tidy(conf.int = T) %>%
  remove_intercept() %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  dplyr::mutate_at(c('estimate', 'conf.low', 'conf.high'), exp) %>%
  as.data.frame() %>%
  condense_fit(estimate_name = "RR (robust SE)")
```

## Ordinal Outcome

### Multinomial Logistic Regression

```{r, echo=FALSE}
trial$trt.factor = factor(trial$trt)
```

```{r}
tbl_regression(nnet::multinom(grade ~ trt.factor, trial), 
               exponentiate = T, 
               label = trt.factor ~ 'Chemotherapy Treatment',
               estimate_fun = ~ style_ratio(.x, digits = 2),
               pvalue_fun = ~ style_pvalue(.x, digits = 2))
```

### Ordinal Logistic Regression

```{r}
broom::tidy(MASS::polr(grade ~ trt.factor, trial, Hess = T), 
            conf.int = T, exponentiate = T, p.values = T) %>%
  dplyr::filter(coef.type == 'coefficient') %>%
  select(term, estimate, conf.low, conf.high, p.value) %>%
  as.data.frame() %>%
  condense_fit(estimate_name = "OR")
```
